Modeling site-specific amino-acid preferences deepens phylogenetic divergence estimates for viral proteins

### 2018-04-16 manuscript/manuscript.tex
updates to the empirical scatter plots

\begin{figure}
\centerline{\includegraphics[width=0.7\textwidth]{figures/empirical_scatter.pdf}}
\caption{\label{fig:empirical_scatter}
\textbf{Effect of site-specific amino-acid preferences and $\Gamma\omega$ rate variation on HA branch length estimation.} 
Points denote the branch lengths between all pairs of tips on the tree. 
Blue and orange denote branches that lead to the H1 and H3 deep mutational scanning reference sequences respectively. 
Each column has ExpCMs defined by a different deep mutational scanning amino-acid preference set. 
(A) The ExpCM defined by the H1, H3, or (H1+H3) average deep mutational scanning amino-acid preferences estimated longer branches from reference sequence used in the deep mutational scanning experiment. 
(B) The addition of $\Gamma\omega$ rate variation leads to more uniform extension of branch length than the addition of site-specific amino-acid preferences.
}
\end{figure}

>>>>

\begin{figure}
\centerline{\includegraphics[width=0.7\textwidth]{figures/empirical_scatter.pdf}}
\caption{\label{fig:empirical_scatter}
\textbf{Modeling site-specific amino-acid preferences using deep mutational scanning experiments does not extend branch lengths uniformly across the HA tree.}
Points denote the branch lengths between all pairs of tips on the tree. 
Blue and orange denote branches that lead to the H1 and H3 deep mutational scanning reference sequences respectively. 
Each column is a different site-specific amino-acid preference set. 
(A) The ExpCMs defined by the H1, H3, or H1+H3 average deep mutational scanning amino-acid preferences estimate longer branches from the reference sequence used in the respective deep mutational scanning experiment. 
(B) The addition of $\Gamma\omega$ rate variation leads to more uniform extension of branch length than the addition of site-specific amino-acid preferences.
}
\end{figure}
